E Coli project paper

### 2013-07-18 paper/paper.tex
even more!

The theory states that the aversion of the FtsZ polymer to the MinC
protein is responsible for the FtsZ polymer setting up in the center
of the cell as opposed to at the cellular poles.  The MinC protein in
turn natrually associates with the minD protein that is modelled in
Huang's differential equations.  \fixme{look this up and write this
  again} The theory is dependent on there being a significant
difference in protein density between the center and polar regions. It
is worthwhile examining this difference in detail.  Figure
\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
fluctuation over time at a point adjacent to the polar cell wall and
at a point adjacent to the cell wall in the center region of the cell.
The different proteins show different relationships between their
maxima and minima.  The MinD-ADP show sharp spikes at the poles and
much smaller oscillations at in the middle.  The values at the poles
are always greater than those in the middle, and the polar peaks
exhibit densities that are roughly 2.5 times greater than the maxima
in the center (\fixme{this factor and the following factor will be put
  into a table of comparisons for each protein and for the different
  cell sizes}).  The MinD-ATP densities show a very different trend.
For these it is the center density that is almost always greater than
the polar density.  The difference in density at the pole versus the
middle is a factor of roughly .85 (once again we'll do this more
officially in a table).  The MinE is similar to the MinD-ADP
comparison.  It shows a difference in maxima by a factor of roughly 2.
The MinC protein is associated with the minD protein, so perhaps the
most important camparison is between the nfl-MinD (MinD protein in all
its forms) at the ends and in the center of the pill.  This shows
sharp spikes at the pills and a maxima difference factor of roughly
1.25. \fixme{I'd like to analyze further what this means for the FtZ
  polymer.  Would a difference like this really have a big effect?
  What sort of effect should it have, looking at experimental data?
  One thing is that Mannik (is it Mannik?) genetically deletes the
  MinC protein and they get 73 percent proper cell division.  It
  really would be good to do a more extensive analysis here,
  referencing what other papers say about this.}

>>>>

The theory states that the aversion of the FtsZ polymer to the MinC
protein is responsible for the FtsZ polymer setting up in the center
of the cell as opposed to at the cellular poles.  The MinC protein in
turn natrually associates with the minD protein that is modelled in
Huang's differential equations.  \fixme{look this up and write this
  again} The theory is dependent on there being a significant
difference in protein density between the center and polar regions. It
is worthwhile examining this difference in detail.  Figure
\ref{frequency-plot-40-20-0-0-150} shows a comparison of density
fluctuation over time at a point adjacent to the polar cell wall and
at a point adjacent to the cell wall in the center region of the cell.
The different proteins show different relationships between their
maxima and minima.  The MinD-ADP show sharp spikes at the poles and
much smaller oscillations at in the middle.  The values at the poles
are always greater than those in the middle, and the polar peaks
exhibit densities that are roughly 2.5 times greater than the maxima
in the center (\fixme{this factor and the following factors will be put
  into a table of comparisons for each protein and for the different
  cell sizes}).  The MinD-ATP densities show a very different trend.
For these it is the center density that is almost always greater than
the polar density.  The difference in density at the pole versus the
middle is a factor of roughly .85 (once again we'll do this more
officially in a table).  The MinE is similar to the MinD-ADP
comparison.  It shows a difference in maxima by a factor of roughly 2.
The MinC protein is associated with the minD protein, so perhaps the
most important camparison is between the nfl-MinD (MinD protein in all
its forms) at the ends and in the center of the pill.  This shows
sharp spikes at the pills and a maxima difference factor of roughly
1.25. \fixme{I'd like to analyze further what this means for the FtZ
  polymer.  Would a difference like this really have a big effect?
  What sort of effect should it have, looking at experimental data?
  One thing is that Mannik (is it Mannik?) genetically deletes the
  MinC protein and they get 73 percent proper cell division.  It
  really would be good to do a more extensive analysis here,
  referencing what other papers say about this.}
